---
title: "Efficient Penguins"
author: "DanSchmutz"
date: "2023-08-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(performance)
```

## Palmer Penguins Analyses


```{r penguins}
pspecies<-'Chinstrap'
pdata<-penguins %>% filter(species==pspecies)

```

This report summarizes what we know from the Palmer Penguins dataset about `r pspecies` penguins.

```{r}
summary(pdata)
```

## Penguin Plots

What island(s) are `r paste(pspecies,"s",sep='')` found on?

```{r island, echo=FALSE}
ggplot(pdata,aes(x=island))+geom_bar()+scale_x_discrete(drop=FALSE)
```

Is there sexual dimorphism in `r paste(pspecies,"s",sep='')`? A violin plot with an overlayed small boxplot can help us find out.

```{r sex, echo=FALSE}
ggplot(pdata,aes(x=sex, y=body_mass_g))+geom_violin()+geom_boxplot(width=.2)
```

Are bill and flipper length related in `r paste(pspecies,"s",sep='')`? A scatterplot with linear smoother and 95% confidence interval guides us.

```{r billflip, echo=FALSE}
ggplot(pdata,aes(x=bill_length_mm, y=flipper_length_mm))+geom_point()+stat_smooth(method='lm')
```

## Linear Statistal Model of bill/flipper relationship
Let's check by making a linear regression.

```{r statmodel, echo=FALSE}
lm1<-lm(flipper_length_mm~bill_length_mm, data=pdata)
summary(lm1)
```

Let's check our assumptions for this model.
```{r assuming, echo=FALSE}
check_model(lm1)
```




